Solutions to Integer Programming from Quantum Annealing

### 2020-05-10 paper/main.tex
add coherence plot

\subsubsection{Decoherence Time}
\label{sec:methods:deco}
Scan over decoherence time

>>>>

\subsubsection{Decoherence Time}
\label{sec:methods:deco}

Mention long coherence time asymptote to right value.

Scan coherence time, match to DWave.

Some more discussion about short coherence time and why it makes sense?

Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence. In this regard, a very short T1 is pushing the systems toward a classical annealing model. The absence of any dephasing is then the best-case quantum annealing model. Consequently, the difference in outcome would trace back to this coherence being present.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./figures/coherence.pdf}
	\caption{asdf}
	\label{fig:prob_mi}
\end{figure}
